IFA Comparison of Noncognitive Skills \\ BCS and MCS

### 2018-02-02 codes/R/cohorts_nc.Rnw
NVQ returns to INT EXT

\begin{table}[ht]
\caption{Estimated latent variable means and covariances} \label{tab:lvpars}
\centering
<<FA_COMP, dependson='FA_SCORES', results='asis'>>=
# compare mean factor scores by gender and cohort

@@

@@

\clearpage
\begin{figure}
\begin{center}
<<AGEHIST, dev='tikz', fig.height=6, fig.width=6, out.width='.6\\linewidth'>>=
@
\end{center}
\caption{Distribution of age in the BCS and MCS sample}
{\scriptsize \emph{Notes}: The figure shows the density of observations at each month of age for each of the two cohorts.  \par}
\end{figure}

>>>>

\begin{table}[ht]
\caption{Estimated means and covariances of scores} \label{tab:scoremeans}
\centering
<<FA_COMP, dependson='FA_SCORES', results='asis'>>=
# compare mean factor scores by gender and cohort

@@

\begin{table}[ht]
\caption{Regression of scores on income} \label{tab:regs}
\centering
\resizebox{\linewidth}{!}{%
<<FA_REGS2, dependson='FA_SCORES', results='asis'>>=
# regress scores on income
library(dplyr)
library(stargazer)

scores2plot$incq_infl <- factor(ntile(scores2plot$faminc_infl, 5))

r.ext.f.c <- lm(EXT ~ faminc_infl*cohort, data=subset(scores2plot, sex=="F"))
r.ext.f.q <- lm(EXT ~ incq_infl*cohort, data=subset(scores2plot, sex=="F"))
r.int.f.c <- lm(INT ~ faminc_infl*cohort, data=subset(scores2plot, sex=="F"))
r.int.f.q <- lm(INT ~ incq_infl*cohort, data=subset(scores2plot, sex=="F"))

r.ext.m.c <- lm(EXT ~ faminc_infl*cohort, data=subset(scores2plot, sex=="M"))
r.ext.m.q <- lm(EXT ~ incq_infl*cohort, data=subset(scores2plot, sex=="M"))
r.int.m.c <- lm(INT ~ faminc_infl*cohort, data=subset(scores2plot, sex=="M"))
r.int.m.q <- lm(INT ~ incq_infl*cohort, data=subset(scores2plot, sex=="M"))

stargazer(r.ext.f.c, r.ext.f.q, r.int.f.c, r.int.f.q, r.ext.m.c, r.ext.m.q, r.int.m.c, r.int.m.q,
          column.labels=c("Females","Males"), column.separate=c(4,4),
          dep.var.caption = "", multicolumn = FALSE,
          omit=c("Constant"),
          covariate.labels=c("Family income (2015 CPI £)",
                             "Family income Q2 (2015 CPI £)",
                             "Family income Q3 (2015 CPI £)",
                             "Family income Q4 (2015 CPI £)",
                             "Family income Q5 (2015 CPI £)",
                             "MCS dummy",
                             "Family income (2015 CPI £) x MCS",
                             "Family income Q2 (2015 CPI £) x MCS",
                             "Family income Q3 (2015 CPI £) x MCS",
                             "Family income Q4 (2015 CPI £) x MCS",
                             "Family income Q5 (2015 CPI £) x MCS"
                             ),
          no.space=TRUE, 
          omit.stat= c("rsq", "f", "ser", "aic", "ll"),
          float=FALSE    # needs begin table outside it
)
@
}
\end{table}

\begin{table}[ht]
\caption{Returns to EXT/INT in BCS} \label{tab:returns}
\centering
\resizebox{\linewidth}{!}{%
<<FA_RETURNS, dependson='FA_SCORES', results='asis'>>=
# regress scores on income
library(dplyr)
library(stargazer)

# get BCS data and make dummy for higher education
scoresBCS <- scores2plot[scores2plot$cohort=="BCS",]
scoresBCS$highered <- as.numeric(scoresBCS$hinvq00>3)
scoresBCS[is.na(scoresBCS$hinvq00), "highered"] <- NA

# females
r.nvq.f <- list()
r.nvq.f[[1]] <- lm(highered ~ EXT + INT, data=subset(scoresBCS, sex=="F"))
r.nvq.f[[2]] <- lm(highered ~ EXT + INT + cog1 + cog2 + cog3, data=subset(scoresBCS, sex=="F"))
r.nvq.f[[3]] <- lm(highered ~ EXT + INT + factor(incq), data=subset(scoresBCS, sex=="F"))
r.nvq.f[[4]] <- lm(highered ~ EXT + INT + ysch_moth + ysch_fath, data=subset(scoresBCS, sex=="F"))
r.nvq.f[[5]] <- lm(highered ~ EXT + INT + factor(incq) + ysch_moth + ysch_fath + cog1 + cog2 + cog3, data=subset(scoresBCS, sex=="F"))

# females
r.nvq.m <- list()
r.nvq.m[[1]] <- lm(highered ~ EXT + INT, data=subset(scoresBCS, sex=="M"))
r.nvq.m[[2]] <- lm(highered ~ EXT + INT + cog1 + cog2 + cog3, data=subset(scoresBCS, sex=="M"))
r.nvq.m[[3]] <- lm(highered ~ EXT + INT + factor(incq), data=subset(scoresBCS, sex=="M"))
r.nvq.m[[4]] <- lm(highered ~ EXT + INT + ysch_moth + ysch_fath, data=subset(scoresBCS, sex=="M"))
r.nvq.m[[5]] <- lm(highered ~ EXT + INT + factor(incq) + ysch_moth + ysch_fath + cog1 + cog2 + cog3, data=subset(scoresBCS, sex=="M"))

stargazer(r.nvq.f[[1]], r.nvq.f[[2]], r.nvq.f[[3]], r.nvq.f[[4]], r.nvq.f[[5]],
          r.nvq.m[[1]], r.nvq.m[[2]], r.nvq.m[[3]], r.nvq.m[[4]], r.nvq.m[[5]],
          dep.var.caption = "Completed Higher Ed. at 30",
          column.labels=c("Females","Males"), column.separate=c(5,5),
          omit=c("Constant"),
          covariate.labels=c("Externalising skill at 5",
                             "Internalising skill at 5",
                             "EPVT Z at 5",
                             "Human figure drawing Z at 5",
                             "Copy design Z at 5",
                             "Family inc. at 10 Q2",
                             "Family inc. at 10 Q3",
                             "Family inc. at 10 Q4",
                             "Family inc. at 10 Q5",
                             "Mother's years of schooling",
                             "Father's years of schooling"
                             ),
          no.space=TRUE, 
          omit.stat= c("rsq", "f", "ser", "aic", "ll"),
          float=FALSE    # needs begin table outside it
)
@
}
\end{table}

\begin{table}[ht]
\caption{Returns to EXT/INT in BCS -- raw scores} \label{tab:returns_raw}
\centering
\resizebox{\linewidth}{!}{%
<<FA_RETURNS_RAW, dependson='FA_SCORES', results='asis'>>=
# regress scores on income
library(dplyr)
library(stargazer)

# get BCS data and make dummy for higher education
scoresBCS <- scores2plot[scores2plot$cohort=="BCS",]
scoresBCS$highered <- as.numeric(scoresBCS$hinvq00>3)
scoresBCS[is.na(scoresBCS$hinvq00), "highered"] <- NA

# females
r.nvq.f <- list()
r.nvq.f[[1]] <- lm(highered ~ EXT.RAW + INT.RAW, data=subset(scoresBCS, sex=="F"))
r.nvq.f[[2]] <- lm(highered ~ EXT.RAW + INT.RAW + cog1 + cog2 + cog3, data=subset(scoresBCS, sex=="F"))
r.nvq.f[[3]] <- lm(highered ~ EXT.RAW + INT.RAW + factor(incq), data=subset(scoresBCS, sex=="F"))
r.nvq.f[[4]] <- lm(highered ~ EXT.RAW + INT.RAW + ysch_moth + ysch_fath, data=subset(scoresBCS, sex=="F"))
r.nvq.f[[5]] <- lm(highered ~ EXT.RAW + INT.RAW + factor(incq) + ysch_moth + ysch_fath + cog1 + cog2 + cog3, data=subset(scoresBCS, sex=="F"))

# females
r.nvq.m <- list()
r.nvq.m[[1]] <- lm(highered ~ EXT.RAW + INT.RAW, data=subset(scoresBCS, sex=="M"))
r.nvq.m[[2]] <- lm(highered ~ EXT.RAW + INT.RAW + cog1 + cog2 + cog3, data=subset(scoresBCS, sex=="M"))
r.nvq.m[[3]] <- lm(highered ~ EXT.RAW + INT.RAW + factor(incq), data=subset(scoresBCS, sex=="M"))
r.nvq.m[[4]] <- lm(highered ~ EXT.RAW + INT.RAW + ysch_moth + ysch_fath, data=subset(scoresBCS, sex=="M"))
r.nvq.m[[5]] <- lm(highered ~ EXT.RAW + INT.RAW + factor(incq) + ysch_moth + ysch_fath + cog1 + cog2 + cog3, data=subset(scoresBCS, sex=="M"))

stargazer(r.nvq.f[[1]], r.nvq.f[[2]], r.nvq.f[[3]], r.nvq.f[[4]], r.nvq.f[[5]],
          r.nvq.m[[1]], r.nvq.m[[2]], r.nvq.m[[3]], r.nvq.m[[4]], r.nvq.m[[5]],
          dep.var.caption = "Completed Higher Ed. at 30",
          column.labels=c("Females","Males"), column.separate=c(5,5),
          omit=c("Constant"),
          covariate.labels=c("Externalising skill at 5 (raw score)",
                             "Internalising skill at 5 (raw score)",
                             "EPVT Z at 5",
                             "Human figure drawing Z at 5",
                             "Copy design Z at 5",
                             "Family inc. at 10 Q2",
                             "Family inc. at 10 Q3",
                             "Family inc. at 10 Q4",
                             "Family inc. at 10 Q5",
                             "Mother's years of schooling",
                             "Father's years of schooling"
                             ),
          no.space=TRUE, 
          omit.stat= c("rsq", "f", "ser", "aic", "ll"),
          float=FALSE    # needs begin table outside it
)
@
}
\end{table}

@@

\clearpage
\begin{figure}
\begin{center}
<<AGEHIST, dev='tikz', fig.height=6, fig.width=6, out.width='.6\\linewidth', cache=TRUE>>=
@
\end{center}
\caption{Distribution of age in the BCS and MCS sample}
{\scriptsize \emph{Notes}: The figure shows the density of observations at each month of age for each of the two cohorts.  \par}
\end{figure}
